Competing Bandits: \\ The Perils of Exploration under Competition

### 2019-02-14 paper/content/introduction.tex
Removed "our prior work".

\xhdr{Discussion.}
The present paper is an experimental counterpart to our prior work \cite{CompetingBandits-itcs18}, which considered a similar duopoly model and obtained a number of theoretical results with ``asymptotic" flavor. For the sake of analytical tractability, that paper makes a somewhat unrealistic simplification that users do not observe any signals about firms' ongoing performance (instead, users choose between firms according to the firms' Bayesian-expected rewards). The high-level conclusion in \cite{CompetingBandits-itcs18} is an inverted-U relationship similar to ours, but the strength of competition is varied in a different way, using assumptions about (ir)rational user behavior.

>>>>

\xhdr{Discussion.}
The present paper is an experimental counterpart to \cite{CompetingBandits-itcs18}, which considered a similar duopoly model and obtained a number of theoretical results with ``asymptotic" flavor. For the sake of analytical tractability, that paper makes a somewhat unrealistic simplification that users do not observe any signals about firms' ongoing performance (instead, users choose between firms according to the firms' Bayesian-expected rewards). The high-level conclusion in \cite{CompetingBandits-itcs18} is an inverted-U relationship similar to ours, but the strength of competition is varied in a different way, using assumptions about (ir)rational user behavior.
